Approximating the Optimal State Abstraction

### 2015-10-08 state_abstraction.tex
beep

% Subsection: Arbitrary reduction in Sample Complexity for a specific MDP.
\subsection{Result 1: Arbitrary reduction in Sample Complexity for a particular MDP.}

% Subsection: More general SC reduction result.
\subsection{Result 2: More general result about sample complexity reduction for MDPs of a certain type}

Q: Assuming a given MDP has property set X, can we say anything about the possible reduction in sample complexity using a state abstraction function.

% Maybe something about exploration.

@@

\begin{itemize}
\item Finding states with {\it exactly} the same Q values, or optimal action and action value, is rare!
\item Can't capture temporal abstraction.
\end{itemize}

@@

@@

Note: Similar to simulation lemma from $E^3$, lets take a look.

@@

In light of Result 3, that state abstraction needs to be defined with respect to some sort of properties about actions, suppose a set of temporally extended actions are included in the action set.

@@

Should be some nice results there.

@@

>>>>

\elem{Result 1:} Arbitrary reduction in Sample Complexity for a particular MDP.

\elem{Result 2:} More general result about sample complexity reduction for MDPs of a certain type

The Question: Assuming a given MDP has property set X, can we say anything about the possible reduction in sample complexity using a state abstraction function.

Possible other Result: Exploration.

@@

\begin{enumerate}
\item Finding states with {\it exactly} the same Q values, or optimal action and action value, or same model, is rare!
\item Can't capture temporal abstraction.
\end{enumerate}

Proposal: Resolve (1) and (2), so that the nice results from Section 2 can be realized. The next two sections talk about how we might go about doing that.

@@

Sort of like the Simulation Lemma from $E^3$.

@@

\subsection{Followup Question:} Why {\it won't} this work for other types of abstractions?
\begin{itemize}
\item Just using state variables...
\item Just Reward function at a state...
\item Just Value of state...
\item Any combination of these...
\end{itemize}

Results about which abstractions {\it don't} work. Note: Already have counter examples for the above 3, would be nice to get more general results.

The result is that we identify which criteria are at the core of making state abstraction {\it useful}.

@@

In light of the above negative results (regarding which abstractions are useful), that state abstraction needs to be defined with respect to some sort of properties about actions, suppose a set of temporally extended actions are included in the action set.

@@

What sort of thing do we want to prove here? Abstractions become temporal if actions are temporally extended? Without temporal extension, forces $T(s,a,s')$ and $R(s,a)$ to do weird things?

Q: Can we treat temporally extended actions in a general enough way to prove things about all possible versions of TEAs, or do we need to do separate proofs for Options/Macroactions?

@@

% --- SECTION: Game Plan ---
\newpage{Game Plan}

First, get results about the approximate state abstraction for each of the 4 under consideration.

Second, investigate temporally extended actions w/ abstraction.

Third, wrap up low hanging fruit results, investigate more general versions of these claims (beyond $\exists MDP s.t. \ldots$.).
